---
title: "Homework 1"
author: "Laya Buchanan"

date: 2020-09-11
output: github_document
---

This is my submission for the first homework assignment for P8105. 

```{r message = FALSE, echo = FALSE}

library(tidyverse)
library(ggplot2)
```

# Problem 1
```{r dataframe creation}
prob1_df = tibble(
  samp = rnorm(10),
  samp_gt_0 = samp > 0,
  char_vec = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J"),
  factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
)
```

Take the mean of each variable in my data frame.

```{r mean pull}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0)) 
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor.

```{r}

as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0)) 
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

```{r}

as.numeric(pull(prob1_df, samp))*pull(prob1_df, samp_gt_0) 
```

# Problem 2

The following code loads the _"penguins"_ dataset:

```{r}
data("penguins", package = "palmerpenguins")

```

This dataset includes the variables:

--------
*   Species
*   Island
*   Bill Length
*   Bill Depth
*   Flipper Length
*   Body Mass
*   Sex
*   Year

This data was collected between the years 2007 and 2009.

The penguin with the longest bill length is a Gentoo penguin from Biscoe with a bill length of 59.6mm.
The mean bill length for all of the penguins in the dataset is `r mean(pull(penguins, bill_length_mm, na.rm = TRUE)`mm. 
 
The penguin with the longest flipper length is a Gentoo penguin from Biscoe with a flipper length of 231mm. The mean flipper length for all of the penguins in the dataset is `r mean(pull(penguins, flipper_length_mm, na.rm = TRUE)`mm. 

The largest penguin is a Gentoo penguin from Biscoe with a mass of 6300g. The mean mass for all penguins in the dataset is `r mean(penguins$body_mass_g, na.rm = TRUE)`g with a standard devation of `r sd(penguins$body_mass_g, na.rm = TRUE)`g.



The code chunk below generates a plot comparing the bill and flipper lengths of the penguins in the dataset color coded by species:


```{r warning = FALSE, message = FALSE}
ggplot(data = penguins,
       aes(x = bill_length_mm, 
           y = flipper_length_mm, 
           color = species))+geom_point(
             
           )
```

Finally, this code saves the plot as a PDF file:

```{r warning = FALSE, message = FALSE}

ggsave("penguin_plot.pdf")

```
