---
title: "Homework 1"
author: "Laya Buchanan"

date: 2020-09-11
output: github_document
---

This is my submission for the first homework assignment for P8105. 

# Problem 2

The following code loads the _"penguins"_ dataset:

```{r}
penguins
```

This dataset includes the variables:
--------
*   Species
*   Island
*   Bill Length
*   Bill Depth
*   Flipper Length
*   Body Mass
*   Sex
*   Year

The penguin with the longest bill length is a Gentoo penguin from Biscoe with a bill length of 59.6mm.
The mean bill length for all of the penguins in the dataset is `mean(penguins flipper_length_mm)`.



The code chunk below generates a plot comparing the bill and flipper lengths of the penguins in the dataset color coded by species:

```{r message = FALSE, echo = FALSE}
library(tidyverse
        )
```

```{r warning = FALSE, message = FALSE}
ggplot(data = penguins,
       aes(x = bill_length_mm, 
           y = flipper_length_mm, 
           color = species))+geom_point(
             
           )
```

Finally, this code saves the plot as a PDF file:

```{r warning = FALSE, message = FALSE}

ggsave("penguin_plot.pdf")

```
