---
title: "Homework 1"
author: "Laya Buchanan"

date: 2020-09-11
output: github_document
---

This is my submission for the first homework assignment for P8105. 

```{r message = FALSE, echo = FALSE}

library(tidyverse)
library(ggplot2)
```

# Problem 1

The code below creates a data frame comprised of a random sample of 10 from a standard normal distribution, a logical vector indicating whether elements of the sample are greater than 0, a character vector of length 10, and a a factor vector of length 10, with 3 different factor “levels.”
```{r dataframe creation}
prob1_df = tibble(
  samp = rnorm(10),
  samp_gt_0 = samp > 0,
  char_vec = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J"),
  factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
)
```




This code takes the mean of each variable in my data frame.

```{r warning = FALSE, message = FALSE}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0)) 
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

The code and results above demonstrate that I can take the mean of numeric and logical variables but not character or factor variables.




The code below converts the variables above to be numeric.
```{r warning = FALSE, message = FALSE, results = "hide"}

as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0)) 
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```
I am able to convert all of the variables types to numeric, expect for the character vector variable.

This code converts the logical vector to numeric, and multiplies the random sample by the result.

```{r}
as.numeric(pull(prob1_df, samp_gt_0))*pull(prob1_df, samp) 
```



The code below converts the logical vector to a factor, and multiplies the random sample by the result.
```{r warning = FALSE, message = FALSE}
as.factor(pull(prob1_df, samp_gt_0))*pull(prob1_df, samp) 
```
The result is not meaningful.



The code below again converts the logical vector to a factor, and then converts the result to numeric, then and multiplies the random sample by the result.
```{r warning = FALSE, message = FALSE}
converted = as.factor(pull(prob1_df, samp_gt_0))*pull(prob1_df, samp) 
as.numeric(converted)*pull(prob1_df, samp)
```
The result is not meaningful because the previous step was not meaningful.


# Problem 2

The following code loads the _"penguins"_ dataset:

```{r}
data("penguins", package = "palmerpenguins")

```

This dataset includes the variables:
--------
*   Species
*   Island
*   Bill Length
*   Bill Depth
*   Flipper Length
*   Body Mass
*   Sex
*   Year

This data was collected between the years 2007 and 2009.


The penguin with the longest bill length is a Gentoo penguin from Biscoe with a bill length of 59.6mm.
The mean bill length for all of the penguins in the dataset is `r mean(pull(penguins, bill_length_mm), na.rm = TRUE)`mm with a standard deviation of `r sd(pull(penguins, bill_length_mm), na.rm = TRUE)`mm. 
 
The penguin with the longest flipper length is a Gentoo penguin from Biscoe with a flipper length of 231mm. The mean flipper length for all of the penguins in the dataset is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`mm with a standard deviation of `r sd(pull(penguins, flipper_length_mm), na.rm = TRUE)`mm.
 

The largest penguin in the dataset is a Gentoo penguin from Biscoe with a mass of 6300g. The mean mass for all penguins in the dataset is `r mean(pull(penguins, body_mass_g), na.rm = TRUE)`g with a standard deviation of `r sd(pull(penguins, body_mass_g), na.rm = TRUE)`g.


The code chunk below generates a plot comparing the bill and flipper lengths of the penguins in the dataset color coded by species:


```{r warning = FALSE, message = FALSE}
ggplot(data = penguins,
       aes(x = bill_length_mm, 
           y = flipper_length_mm, 
           color = species))+geom_point(
             
           )
```

Finally, this code saves the plot as a PDF file:

```{r warning = FALSE, message = FALSE}

ggsave("penguin_plot.pdf")

```
